Normalized Coherence

### 2019-09-17 Analysis/Normalized_Coherence.Rmd

>>>>

# Getting all msig pathway slopes for string (Used in Supplementary Table 2)

```{r}
#Re-read msig
msig = msigdbr()

# Define all categories
all_cats = unique(msig$gs_subcat)

#Remove empty categories
all_cats = subcats[which(subcats!="")]

#Get slopes
msig_frame_string_all = get_msig_slopes(sub_cats = all_cats, database = string)

#Save results
saveRDS(msig_frame_string_all, "./data/coherence_results/All_Msig_String.rds")

```
